### 2021-05-28 chapters/2_introduction.tex
v1.0 RQ1

\subsection{Research questions}
To reduce the cost of mutation testing, we try to find a solution that can cluster mutants while maintaining the accuracy of the same complete set of mutants. 
Our goal is to cluster any mutant that is generated.
We will do this with two different approaches.
Our first approach will be a qualitative approach and second a quantitative approach. 
We structure our research on the following research questions:
\newline
\textbf{Research Question 1}: What set of characteristics can we identify for clustering generated mutants to reduce the amount executed, while maintaining effectiveness?
\newline
\textbf{Research Question 1.1}: How do the existing mutation testing tools for Java compare to each other?
\newline
\textbf{Research Question 2}: How can we train a machine learning model to recognize and cluster generated mutants to reduce the amount executed, while maintaining effectiveness?

\subsection{Research method}
We start with comparing existing mutation testing tools. 
We will use the existing literature as a starting point and research what would be the best tool to use for this thesis.
\newline
After we have selected a tool we will research existing clustering techniques.
Based on the results of this research we select and implement one or more clustering algorithm that will cluster mutants. 
One or more mutants of each cluster will be executed by the mutation tooling.
We will then compare the mutation score of the clustered mutants with the mutation score of a full set of mutants.
\newline
To answer our second research question we will train a machine learning model to cluster mutants.
We can then repeat the comparison we did for research question one. 
\newline
We want to see how the algorithm/model performs on big and small projects.
These project must also require a test suite.
\newline
We chose to focus on projects that use Java as main programming language because it is one of the most popular languages\cite{Tiobe}.

>>>>

To reduce the cost of mutation testing, we try to find a solution that can cluster mutants while maintaining the accuracy of the same complete set of mutants. 
Our goal is to cluster any mutant that is generated.
We will do this with two different approaches.
Our first approach will be a qualitative approach and second a quantitative approach. 
We structure our research on the following research questions:
\newline
\textbf{Research Question 1}: What set of characteristics can we identify for clustering generated mutants to reduce the amount executed, while maintaining effectiveness?
\newline
\textbf{Research Question 1.1}: How do the existing mutation testing tools for Java compare to each other?
\newline
\textbf{Research Question 2}: How can we train a machine learning model to recognize and cluster generated mutants to reduce the amount executed, while maintaining effectiveness?
\newline
We start with comparing existing mutation testing tools. 
We will use the existing literature as a starting point and research what would be the best tool to use for this thesis.
\newline
After we have selected a tool we will research existing clustering techniques.
Based on the results of this research we select and implement a clustering algorithm that will cluster a characteristic of the mutants. 
One or more mutants of each cluster will be executed by the mutation tooling.
We will then compare the mutation score of the clustered mutants with the mutation score of a full set of mutants.
\newline
To answer our second research question we will train a machine learning model to cluster mutants.
We can then repeat the comparison we did for research question one. 
\newline
We want to see how the algorithm/model performs on big and small projects.
These project must also require a test suite.
\newline
We chose to focus on projects that use Java as main programming language because it is one of the most popular languages\cite{Tiobe}.

### 2021-05-28 chapters/3_background.tex
Starting with rq1 writeup
v1.0 RQ1

\chapter{Background}
\label{ch:background}
This chapter will present the necessary background information for this thesis. First, we define some basic terminology that will be used throughout this thesis.
Next, we will compare existing mutation testing tools. We start of by reviewing existing literature and then extend the comparison. \todo{extend this later on?}
\section{Terminology}
\todo{do this when we finished experiments and all}
\todo{subsuming mutants}
\todo{levensteihn distance}
\todo{maven and gradle}
\section{Project selection}
We chose two main requirements for selecting software projects; the projects should have a test suite and the test suite should not contain failing tests.
We started out by selecting projects that were also used in other research within the mutation testing and testing domain\cite{Pizzoleto2019,Yu2019PossibilityScope,Wei2021SpectralTesting, Zhang2019PredictiveTesting, Chen2018SpeedingStudy, Laurent2017AssessingPIT}.
This resulted in six projects that satisfied the requirements.
To extend our sample of projects we selected projects from the first six pages of the most popular Java projects on GitHub\footnote{\url{https://github.com/search?p=7&q=language\%3Ajava+stars\%3A\%3E10000&type=Repositories}}.
From this selection we filtered out all the projects that contained failing tests that weren't libraries or applications.
We ended up with a total sample of 21 projects. 
These projects consists of Java libraries, Android libraries and Java applications.

>>>>

\chapter{Background}
\label{ch:background}
This chapter will present the necessary background information for this thesis. First, we define some basic terminology that will be used throughout this thesis.
Next, we will compare existing mutation testing tools. We start of by reviewing existing literature and then extend the comparison. \todo{extend this later on?}
\section{Terminology}
\todo{do this when we finished experiments and all}
\todo{subsuming mutants}
\todo{levensteihn distance}
\todo{maven and gradle}
\section{Project selection}
We choose three main requirements for selecting software projects; the projects should have a test suite, the test suite should not contain failing tests and the mutation testing tool should be able to execute mutants for the sample project.
We selected projects that were also used in other research within the mutation testing and testing domain\cite{Pizzoleto2019,Yu2019PossibilityScope,Wei2021SpectralTesting, Zhang2019PredictiveTesting, Chen2018SpeedingStudy, Laurent2017AssessingPIT}.
We extend our sample by selecting projects from the first six pages of the most popular Java projects on GitHub\footnote{\url{https://github.com/search?p=7&q=language\%3Ajava+stars\%3A\%3E10000&type=Repositories}}.
The unfiltered sample contains 50+ projects.
From there we filter out all the projects that contain failing tests and that aren't libraries or applications.
The result consists of a sample with sixteen projects in total.
